\documentclass[11pt]{article}

\usepackage[margin=1cm]{geometry}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=magenta]{hyperref}
\usepackage{parskip}
\usepackage{units}  % for \nicefrac{num}{den}

\setlist{itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt}

\begin{document}
	\begin{center}\begin{huge}\underline{\textbf{Green Chicken Enchiladas}}\end{huge}\end{center}

	\section*{Ingredients}
	\begin{itemize}
		\item 2 lbs chicken breast
		\item 12 (10-inch) flour tortillas
		\item 1 (8-ounce) package shredded Monterey Jack cheese
		\item 2 (15-ounce) cans green enchilada sauce
		\item 1 tsp onion powder
		\item 1 tsp garlic powder
		\item \nicefrac{3}{4} tsp ancho chile powder
		\item \nicefrac{3}{8} tsp chipotle chile powder
		\item 1 tsp salt
		\item pepper, to taste
		\item canola oil, to coat chicken
		\item sour cream (optional)
		\item hot sauce (optional)
	\end{itemize}
	
	\section*{Instructions}
	\begin{enumerate}
		\item Bake chicken, covered in a thin coat of oil, in the oven at 350$^\circ$F until 165$^\circ$F internal, about 30 minutes.
		\item Preheat oven to 350$^\circ$F.
		\item Shred chicken in a large bowl.
		\item Add one can of enchilada sauce along with garlic powder, onion powder, ancho chile powder, and chipotle chile powder.
		\item Lightly grease an 11" by 7" baking dish.
		\item Fill each tortilla with equal amounts of chicken and cheese, reserving 1/4 cup cheese for topping. Roll tortillas to form enchiladas. Arrange enchiladas in the prepared baking dish. Cover with the other can of enchilada sauce.
		\item Bake enchiladas, covered with aluminum foil, 30 minutes in the preheated oven. Top with reserved cheese, and continue baking 5 minutes, until cheese is melted.
		\item Remove from oven and serve with sour cream and hot sauce if desired.
	\end{enumerate}
	
	\section*{Notes}
	
\end{document}
