\documentclass[11pt]{article}

\usepackage[margin=1cm]{geometry}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=magenta]{hyperref}
\usepackage{parskip}
\usepackage{units}  % for \nicefrac{num}{den}

\setlist{itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt}

\begin{document}
	\begin{center}\begin{huge}\underline{\textbf{Beef Stir Fry}}\end{huge}\end{center}

	\section*{Ingredients}
	Stir fry:\vspace*{-1.5ex}
	\begin{itemize}
		\item 1\nicefrac{1}{2} Tbsp sesame cooking oil
		\item 2 lbs ground beef \textit{(90\% lean)}
		\item 1 yellow onion, thinly sliced
		\item 1 red bell pepper, thinly sliced
		\item 1 carrot, washed and grated
		\item 32 oz. broccoli
		\item salt and pepper to taste
	\end{itemize}
	
	Sauce:\vspace*{-1.5ex}
	\begin{itemize}
		\item \nicefrac{1}{4} cup low sodium soy sauce
		\item 2 Tbsp rice vinegar
		\item 70 g brown sugar
		\item 1.5 tsp xanthan gum \textit{(optional, can be found in HEB bulk section)}
		\item 3 tsp toasted sesame oil
		\item 5 garlic cloves, minced \textit{(3 tsp)}
		\item 15 g ginger, minced \textit{(2 tsp)}
		\item \nicefrac{1}{2} tsp chili flakes
	\end{itemize}
		
	Garnish:\vspace*{-1.5ex}
	\begin{itemize}
%		\item 1 spring onion
		\item sesame seeds \textit{(optional)}
	\end{itemize}
		
	Jasmine Rice:\vspace*{-1.5ex}
	\begin{itemize}
		\item 1\nicefrac{1}{2} cups jasmine rice, washed
		\item 2 cups water
		\item salt to taste
	\end{itemize}
	
	\section*{Instructions}
	Rice:
	\begin{enumerate}
		\item Put the rice and water into a rice cooker and start that hoe.
	\end{enumerate}
	
	Sauce:
	\begin{enumerate}
		\item Mix the toasted sesame oil and xanthan gum, making sure to leave no clumps.
		\item Mix all the sauce ingredients together, adding the xanthan gum mixture last and stirring vigorously.
	\end{enumerate}
	
	Stir fry:
	\begin{enumerate}
		\item Fry the onion until soft.
		\item Add beef and cook until browned, seasoning with salt and pepper.
		\item Add veggies and cook until just softened.
		\item Add sauce and cook until reduced.
		\item Add sesame seeds. \textit{(optional)}
		\item Adjust seasoning as necessary.
	\end{enumerate}
	
%	Garnish:
%	\begin{enumerate}
%		\item onon
%	\end{enumerate}
	
	\section*{Notes}
	I made a few changes from the original.
	
	Links:
	\begin{enumerate}
		\item\href{https://www.youtube.com/watch?v=kBivrTwvTVU}{Original YouTube Recipe} 
	\end{enumerate}
	
\end{document}
