\documentclass[11pt]{article}

\usepackage[margin=1cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{units}  % for \nicefrac{num}{den}

\setlist{itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt}

\begin{document}
	\begin{center}\begin{huge}\underline{\textbf{Taco Tot Casserole}}\end{huge}\end{center}

	\section*{Ingredients}
	\begin{itemize}
		\item 1 pound of 90\% lean ground beef
		\item 1 yellow onion, diced
		\item 1 oz. taco seasoning
		\item \nicefrac{1}{2} tsp kosher salt
		\item 1 15-oz. can of corn
		\item 1 15-oz. can of black beans, drained
		\item 8 oz. shredded Mexican cheese
		\item 1 32-oz. bag of frozen tater-tots
		\item \nicefrac{1}{2} cup sour cream
		\item 2 Tbsp hot sauce
		\item 2 Tbsp lime juice
		\item 1 ripe avocado, coarsely diced
		\item 1 tomato, diced
		\item 1 jalape\~{n}o, thinly sliced
	\end{itemize}
	
	\section*{Instructions}
	\begin{enumerate}
		\item Preheat oven to 400°F. Heat a large skillet over medium-high. Add ground beef, onion, taco seasoning, and salt; cook, stirring to crumble, until browned, 8 to 10 minutes. Remove from heat. Stir in corn, beans, green chiles, and 1 cup of the cheese.
		
		\item Spoon mixture into a lightly greased 9- x 13-inch baking dish. Place potato tots in an even layer on top of mixture.
		
		\item Bake, uncovered, in preheated oven until tots are golden brown and crispy, 35 to 40 minutes. Sprinkle with remaining 1 cup cheese. Bake until cheese is melted, about 5 minutes.
		
		\item Whisk together sour cream, hot sauce, and lime juice. Drizzle casserole with sour cream mixture; top with avocado, tomato, and jalapeño.
	\end{enumerate}
	
	\section*{Notes}
	Links:
	\begin{enumerate}
		\item \href{https://www.myrecipes.com/recipe/taco-tot-casserole}{Online recipe}
	\end{enumerate}
	
\end{document}
