\documentclass[11pt]{article}

\usepackage[margin=1cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\setlist{itemsep=1pt, topsep=0pt, parsep=0pt, partopsep=0pt}

\begin{document}
	\begin{center}\begin{huge}\underline{\textbf{Chicken Tikka Masala}}\end{huge}\end{center}

	\section*{Ingredients}
	Chicken:\vspace*{-1.5ex}
	\begin{itemize}%\setlength\itemsep{0em}
		\item 1 cup full-fat yogurt
		\item 2 tsp kosher salt
		\item 1.25 Tbsp garam masala
		\item 1 tsp Kashmiri chili powder
		\item 2.5 tsp minced garlic
		\item 0.25 tsp minced ginger
		\item 2 lbs boneless skinless chicken thighs, \underline{cut into 1" pieces}
	\end{itemize}

	Sauce:\vspace*{-1.5ex}
	\begin{itemize}
		\item 3 Tbsp vegetable oil
		\item 1 large yellow onion, thinly sliced
		\item 0.25 tsp minced ginger
		\item 1.5 tsp minced garlic
		\item 1 tsp Kashmiri chili powder
		\item 1 Tbsp garam masala
		\item 2 tsp sugar
		\item 1 tsp ground cumin
		\item 28 oz. can of crushed tomato
		\item 1 cup heavy cream
		\item 8 oz. coconut milk (shake well!)
		\item salt to taste
	\end{itemize}

	\section*{Instructions}
	Chicken:
	\begin{enumerate}
		\item In a medium-sized bowl: add yogurt, salt, garam masala, paprika, garlic, and ginger; whisk to combine. Next, add chicken to your bowl, toss to coat thoroughly, and marinate for 10 minutes or overnight in the fridge.
	\end{enumerate}
	Sauce:
	\begin{enumerate}
		\item Set a 10-inch pan over medium-high heat, and add enough vegetable oil to coat the bottom of the pan. Once hot and nearly smoking, add all your chicken in batches and sear for 2 - 3 minutes per side until nicely browned on all edges.
		\item Remove chicken, add additional oil if needed, and lower the heat to medium. Add onion, ginger, and garlic. Season lightly with salt, and saute for 3 - 5 minutes, stirring occasionally, until softened. Next, add paprika, cayenne, garam masala, and sugar; saute until fragrant, about 30 seconds.
		\item Add crushed tomatoes, stir and reduce for 5 minutes. Optionally, pour into a blender and blend on high speed until as smooth as possible. Place back in the pot, reduce the heat to low, add all your chicken, and simmer, stirring occasionally, for 10 minutes or until the chicken is thoroughly cooked and the sauce is reduced.
		\item Stir in heavy cream and reduce for 7 - 8 more minutes or until the sauce is thick and velvety—adjust salt levels if necessary. Serve immediately with steamed white rice.
	\end{enumerate}

	\section*{Notes}
	Links:
	\begin{enumerate}
		\item \href{https://www.joshuaweissman.com/post/2-chicken-tikka-masala-but-cheaper}{Original recipe}
		\item\href{https://youtu.be/O5l1SMavklI}{Original recipe video}
	\end{enumerate}

\end{document}