\documentclass[11pt]{article}

\usepackage[margin=1cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{units}  % for \nicefrac{num}{den}

\setlist{itemsep=1pt, topsep=-1ex, parsep=0pt, partopsep=0pt}

\begin{document}
	\begin{center}\begin{huge}\underline{\textbf{Korean Beef Skillet}}\end{huge}\end{center}
	
	Makes 8 servings.

	\section*{Ingredients}
	\vspace{-1ex}
	\begin{itemize}
		\item 4 Tbsp sesame oil
		\item 2 pounds ground beef (96\% lean is a good idea--less draining needed)
		\item 1 tsp minced ginger
		\item 4 Tbsp chili-garlic paste
		\item \nicefrac{1}{2} cup brown sugar
		\item \nicefrac{1}{2} cup soy sauce
		\item 1 \nicefrac{1}{2} cups sliced green onions
		\item 8 cups sliced cucumbers
		\item 2 tsp sesame seeds
		\item 3 cups kimchi (this is good on its own, but sorta gross to throw in some cauliflower rice...)
		\item 8 cups cooked cauliflower rice
		\item Salt and pepper, to taste
	\end{itemize}
	
	\section*{Instructions}
	\begin{enumerate}
		\item In a bigass skillet, heat 2 Tbsp sesame oil over medium-high heat. Cook and crumble ground beef until browned. Drain excess fat. Stir in ginger, chili-garlic paste, brown sugar, and soy sauce. Cook until heated, about 4 minutes. Transfer to 1-cup section of meal prep containers. Garnish with half of the green onions.
		\item In a large bowl, toss cucumbers with 2 Tbsp sesame oil and sesame seeds. Salt and pepper to taste. Transfer to second 1-cup section of meal prep containers.
		\item In a large bowl, toss together kimchi, cauliflower rice and remaining green onions. Spoon into 2-cup section of meal prep containers. Refrigerate until ready to reheat and enjoy.
	\end{enumerate}
	
	\section*{Notes}
	Recipe was from a cute lil insert that came with my meal prep containers :)\\
	More meal prep recipes available \href{https://www.goodcook.com/recipes/category/meal-prep}{here.}
	
\end{document}
