\documentclass[11pt]{article}

\usepackage[margin=1cm]{geometry}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=magenta]{hyperref}
\usepackage{parskip}
\usepackage{units}  % for \nicefrac{num}{den}

\setlist{itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt}

\begin{document}
	\begin{center}\begin{huge}\underline{\textbf{Chicken and Sausage Gumbo}}\end{huge}\end{center}
	
	Servings: 8-10\\
	Prep time: 20 mins\\
	Total time: 4 hours\\
	
	*Requires an 8-quart cooking vessel (recipe can be halved of course)

	\section*{Ingredients}
	\begin{itemize}
		\item 2 lbs chicken thighs
		\item 2 lbs andouille sausage, coined
		\item 1 cup all-purpose flour
		\item 1 cup + 2 tbsp canola oil
		\item 4 ribs celery, diced
		\item 2 jalape\~nos, seeded and minced (slice outside seam-to-seam)
		\item 2 small green bell peppers, diced (slice outside seam-to-seam)
		\item 2 small yellow onions, diced (radial chop)
		\item 12 garlic cloves, minced (3 Tbsp)
		\item 2 cups amber beer
		\item 8 cups chicken stock
		\item 2 tsp fresh thyme
		\item 8 bay leaves
		\item cayenne pepper, to taste
		\item kosher salt to taste
		\item freshly ground black pepper to taste
		\item cooked white rice, for serving
	\end{itemize}
	
	\section*{Instructions}
	\begin{enumerate}
		\item Cut up the vegetables and sausage.
		\item Season the chicken with salt, (a lot of) black pepper, and two tablespoons of canola oil. Broil until slightly charred and golden, about 10 minutes, and set aside.
		\item Heat a thick-bottomed 8-quart Dutch oven over medium. Add the remaining oil and flour and, using a whisk, stir \textit{constantly}, until the roux has turned chocolate brown, about 25 minutes (shorter or longer depending on how hot you're cooking).
		\item Add the vegetables (but not the garlic) along with a pinch of salt, and cook until onions start to get translucent. Add the garlic and cook until onions are translucent. Add the beer and stir vigorously for a couple minutes to form the gravy. \textbf{Slowly} stir in the stock. Add thyme, bay leaves, $\sim$1 Tbsp salt, and $\sim$30 cracks of black pepper. Add chicken thighs and sausage and simmer for 3 hours, stirring occasionally. Season to taste with salt, black pepper, and cayenne pepper, and serve with cooked rice.
	\end{enumerate}
	
	\section*{Notes}
	If you are not careful while adding the stock, you will break your beautiful roux. I've found that if you start real slow and keep things real hot, you're less likely to break the roux.
	
	Links:
	\begin{enumerate}
		\item \href{https://www.vice.com/en/article/z489zy/chicken-and-andouille-sausage-gumbo}{Online recipe} (The dumbasses at Vice engaged in their characteristic move of being objectively wrong. My recipe is a corrected version of theirs that actually stays true to the instructions and proportions in the video, which is the original recipe.)
		\item \href{https://www.youtube.com/watch?v=76JXtB7JFQY}{Recipe video} 
	\end{enumerate}
	
\end{document}
