\documentclass[11pt]{article}

\usepackage[margin=1cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{units}  % for \nicefrac{num}{den}

\setlist{itemsep=1pt, topsep=-1ex, parsep=0pt, partopsep=0pt}

\begin{document}
	\begin{center}\begin{huge}\underline{\textbf{Irish Beef Stew}}\end{huge}\end{center}
	
	TODO: Add the proper dutch oven approach. The instant pot version didn't turn out so good.
	
	Also, buy your own chuck roast so you can cut your own stew meat. Pre-cut stew meat has fatty chunks and some of the pieces aren't fully separated.
	
	Also, don't put the bacon in it (TODO). It gets all soggy and gross.
	
	Also, the recipe seems to be a bit too acidic (sour!).
	
	Makes 8 servings.
	
	Prep time: TODO\\
	Cook time: TODO\\
	Total time: TODO

	\section*{Ingredients}
	\begin{itemize}
		\item 12 oz. Thick-cut bacon
		\item 2 \nicefrac{1}{2} pounds boneless beef chuck roast, cut into 1 \nicefrac{1}{2}- to 2-in. chunks
		\item 1 Tbsp kosher salt
		\item 1 tsp black pepper (or more ;))
		\item 3 medium yellow onions, cut into quarters through the root
		\item 8 oz. baby carrots
		\item 8 oz. celery
		\item 4 tsp minced garlic
		\item 8 thyme sprigs
		\item \nicefrac{1}{4} cup tomato paste
		\item 2 Tbsp all-purpose flour
		\item 1 bottle (11.2 oz) Guinness draught/stout
		\item 2 \nicefrac{1}{2} cups beef broth
		\item 12 oz. baby red potatoes, halved (quartered, if large)
		\item 1 Tbsp country Dijon mustard
		\item \nicefrac{1}{4} cup chopped fresh flat-leaf parsley
		\item 1 tsp lemon zest
		\item Crusty bread (personal preference), for serving
		\item Salted Irish butter, for serving
	\end{itemize}
	
	\section*{Instructions}
	Bacon:
	\begin{enumerate}
		\item Line a baking sheet with aluminum foil, and place a wire cooling rack in the baking sheet.
		\item Lay the strips of bacon on the cooling rack. They can touch, but they shouldn't overlap.
		\item Place the baconated baking sheet in a cold oven, and set the oven to 400 $^\circ$F. Cook for $\sim$20 minutes, to desired crispness. Transfer bacon to a plate. Reserve drippings in heat-proof container.
	\end{enumerate}
	\vspace{1ex}
	
	Quick and Dirty (Instant Pot):
	\begin{enumerate}
		\item Toss beef chunks with salt and pepper. Set Instant Pot to Saute on the ``more" setting. Add 2 tablespoons of the reserved drippings to Instant Pot; swirl to coat. Add half of the beef in an even layer, and cook until browned on all sides. Transfer browned beef to bacon plate and repeat with remaining drippings and beef.
		\item Add onions to Instant Pot and set Saute to the ``normal" setting. Cook until browned, about 3 minutes. Add tomato paste and cook, stirring constantly, until onions are coated, about 1 minute. Add flour and cook until evenly coated and toasted, about 1 minute. Add Guinness and cook until thickened and reduced, about 3 minutes. Add broth, carrots, celery, garlic, thyme, potatoes, browned beef, and bacon.
		\item Put the Instant Pot's lid on and pressure cook on ``normal" with ``high" pressure for 20 minutes (It may take about 15 minutes for the pot to pressurize). Quick-release pressure (should take about 5 minutes) and uncover. Stir in mustard.
		\item While stew cooks, stir together parsley and lemon zest. Sprinkle over each serving. Serve hot with crusty bread and salted butter.
	\end{enumerate}
	\vspace{1ex}
	
	Slow and Steady (Traditional):
	\begin{enumerate}
		\item TODO
	\end{enumerate}
	\vspace{1ex}
	
	\section*{Notes}
	I like ciabatta bread :)\\\\ \href{https://web.archive.org/web/20200811194325/https://www.myrecipes.com/recipe/irish-beef-stew-with-guinness}{Original recipe}
	
\end{document}
